---
title: "Demonstrating the PCT, for education and reproducibility"
output: github_document
---

Welcome to pct-demo, a small repo with a little code and data to how how the pct works.

The starting point is that regional data has already been generated.
See [pct-scripts](https://github.com/pctbike/pct-scripts) or an academic paper on the subject ([Lovelace et al. 2017](https://www.jtlu.org/index.php/jtlu/article/view/862)).

We also assume your have R and RStudio installed and running on your computer.
There is plenty of guidance online, notably on the RStudio website:  [rstudio.com](https://www.rstudio.com/products/rstudio/download/).

The first step is to download the the repo https://github.com/npct/pct-demo/archive/master.zip - that contains both code and data.
Note that it contains a .qgs file that can be opened with the open source program [QGIS](http://qgis.org/) - another powerful tool for analysing the geographical distribution of cycling potential.

The remainder of this tutorial is based on R code, which can be found in the [code](https://github.com/npct/pct-demo/tree/master/code) folder.
We encourage you to look over these scripts.
The script to load-in the data, for example, can be opened with the following command:

```{r, eval=FALSE}
file.edit("code/load-data.R")
```

Once that file is open we can run it line-by-line, e.g. by pressing `Ctl-Enter`.
Alternatively you can entirety of a script file with the `source()` function.

There are some dependencies: you need to have some packages installed.

```{r}
source("code/set-up.R")
```


To load the input data, we can run the following script:

```{r}
source("code/load-data.R")
```



## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
